Setting the Stage to Understand the Roles in Software Organizations:\\ A Framework and a Case Study

### 2011-09-29 soulgem.tex
Tiny change to abstract. Submitted version.

Software professionals divide their work by roles, but to date, researchers have not examined nor questioned the nature of these roles, which is a potential source of misunderstandings and confusion. To address this, we formulate a theoretical framework based on sociological and organizational research, in which roles are defined as sets of expectations placed on the members of the software organization.

>>>>

Software professionals divide their work by roles, but to date, researchers have not examined nor questioned the nature of these roles, which is a potential source of confusion. To address this, we formulate a theoretical framework based on sociological and organizational research, in which roles are defined as sets of expectations placed on the members of the software organization.
